ASHA 2023 Listening Effort Data Analysis

### 2023-10-26 ASHA 2023 Analysis/data_analysis.Rmd
Started counts for accurate vs inaccurate responses
need to investigate why number of trials does not equal number of expected trials

>>>>

# Load in cleaned data

data <- rio::import("Cleaned Data/cleaned_data.csv")

# Selecting relevant variables to explore phrase accuracy and perceived listening effort
data1 <- data %>%
  dplyr::select(subject, trial, speaker, effort_rating, rep_acc) %>%
  dplyr::distinct()

# Calculating repetition accuracy descriptive data

rep_acc <- data1 %>%
  dplyr::group_by(speaker, rep_acc) %>%
  dplyr::summarize(n = n())
